Impact of journal data archiving mandates on author attitudes, experiences,

### 2018-03-21 manuscript.Rmd
updates

---
title: "Data Archiving Attitudes"
author: "Heather A. Piwowar, Todd J. Vision"
date: "March 20, 2018"
output:
  html_document:
    css: style.css
    fig_caption: yes
    keep_md: yes
    number_sections: yes
    toc: yes
  md_document:
    variant: markdown_github
  pdf_document:
    fig_caption: yes
    number_sections: yes
    toc: yes
  word_document:
    fig_caption: yes
csl: peerj.csl
bibliography: input_references.bib
---

@@

[TODO: LIST THE JOURNALS IN CONTROL AND JDAP ARMS]

@@

@@

@@

some more: `r citep(c(
bib["2015thank-y"],
bib["anagnostou2015when-da"],
bib["nosek2015scienti"],
bib["stodden2018an-empi"],
bib["budin-ljosne2014data-sh"],
bib["hate2015sweat-s"],
bib["naudet2018data-sh"],
bib["curty2017attitud"],
bib["linek2017data-sh"],
bib["longo2016data-sh"],
bib["berger2016iscbs-i"],
bib["chigusa2017state-o"],
bib["womack2015researc"],
bib["doi:10.1002/asi.23917"],
bib["plos-medicine-editors2016can-dat"],
bib["van-tuyl2016water-w"],
bib["vasilevsky2017reprodu"],
bib["doi:10.1002/asi.23336"],
bib["pearce2011data-sh"],
bib["alsheikh-ali2011public-"],
bib["vines2013mandate"],
bib["roche2014trouble"],
bib["roche2015public-"],
bib["lin2014recomme"],
bib["whitlock2016a-balan"],
bib["naughton-l2016making-"],
bib["teunis2015do-corr"],
bib["fetterman2015the-rep"]
))
`

@@

- IRB
- Survey questions
- Instructions to authors
- Contact corresponding code
- Comparison journals spreadsheet
- R files
- Raw data

@@

@@

table <- subset(relevant_jdap_adoption_dates, policy == "Required")[,c('JournalName','policy_start_str')]
colnames(table) <- c('Journal', 'Adoption Date of JDAP or Equivalent Policy')
rownames(table) <- NULL
kable(table)

>>>>

---
title: Impact of journal data archiving mandates on author attitudes, experiences,
  and practices
author: "Heather A. Piwowar, Todd J. Vision"
csl: peerj.csl
output:
  md_document:
    variant: markdown_github
  html_document:
    css: style.css
    fig_caption: yes
    keep_md: yes
    number_sections: yes
    toc: yes
  pdf_document:
    fig_caption: yes
    number_sections: yes
    toc: yes
  word_document:
    fig_caption: yes
bibliography: input_references.bib
---

@@

@@

|position	| number of responses	| proprotion of responses |
| ---       | ---           | --- |
|postdoc|	        1049|	0.254|
|tenured faculty|	986|	0.239|
|(blank)|	        696|	0.169|
|research staff|	470|   	0.114|
|non-tenured faculty|	463|	0.112|
|student|	        343|	0.083|
|Other (please specify)|	117|	0.028|
|Grand Total|	4124|	1|

Journal policies as of December 2014:

|journal	| policy start	| number of responses |
| ---       | ---           | --- |
|American Naturalist|2011-01-01|115|
|Animal Behaviour||129|
|Behavioral Ecology||62|
|Behavioral Ecology and Sociobiology||78|
|Biological Conservation||134|
|Biological Journal of the Linnean Society|2011-09-03|102|
|Biology Letters|2014-10-29|80|
|BMC Biology|2014-08-19|22|
|BMC Evolutionary Biology||102|
|BMC Plant Biology||53|
|Conservation Biology||71|
|Conservation genetics||64|
|Ecological Applications|2014-01-01|115|
|Ecological Monographs|2011-01-01|25|
|Ecology||156|
|Evolution|2011-01-01|115|
|Evolutionary Applications|2011-01-01|22|
|Evolutionary Ecology||38|
|FASEB Journal||143|
|FEBBS Letters||113|
|Functional Ecology|2012-12-05|59|
|GENETICS|2010-01-01|95|
|Genome research|2008-07-06|70|
|Global Change Biology||124|
|Heredity|2011-03-01|42|
|ISME Journal||66|
|Journal of Animal Ecology|2012-12-01|68|
|Journal of Biogeography||70|
|Journal of Ecology|2013-06-03|74|
|Journal of Evolutionary Biology|2011-10-24|96|
|Journal of Experimental Biology||179|
|Journal of Experimental Botany||123|
|Journal of Heredity|2013-01-01|32|
|Journal of Molecular Evolution||23|
|Journal of Paleontology||34|
|Molecular Biology and Evolution|2010-12-31|104|
|Molecular Ecology|2011-01-01|154|
|Molecular Phylogenetics and Evolution||83|
|Nature structural & molecular biology||50|
|New Phytologist|2010-11-23|80|
|Oecologia||151|
|Oikos|2014-03-06|118|
|Paleobiology||2|
|Physiological Genomics||38|
|PLoS Biology|2014-11-14|82|
|Proceedings of the Royal Society B: Biological Sciences|2013-03-20|217|
|Systematic Biology|2010-12-31|26|
|The Plant Journal|2010-08-18|102|

@@

### Free text comments

There were 356 free text comments. A few representative ones:

- You may wish to consider fields of research. In ecology I guard my data; for evolutionary studies I use online data. The fields have very different attitudes and approaches.
- In ecology, we often spend years collecting datasets that are unique.  That effort, combined with the set of ideas that led to collection of the data, should convey a large degree of 'ownership'.  
- Thanks for researching this question.  I cannot share my data...  unless someone directly requests it and guarantees shared authorship of the product.  We invested tremendous amounts of money and personal effort in collecting and grooming these data, so we need to work through all the associated papers before others have a chance.
- I think you could have more comments related to how cumbersome, time-consuming, and expensive this new requirement is to most researchers.
- Putting the data into an archive will produce additional costs. How is going to pay for it? At the moment, we are rquested to keep the data for at least 10 years, and share them with colleagues upon request. This has worked so far, and I think we should leave it at that and not use up extra money that could be better used for funding science. 
- Science is about sharing ideas and data. If we don't do this it is not science. It's pretty simple. The only question is which datasets is it worth investing effort into sharing at what level of detail and standards. This is tricky to get the balance right but this debate should not negate the premise that we're about data sharing.
- I personally find submitting your own data a bit tedious, and I would always be worried that someone would use arcane statistical models to contradict something I found, but in the end transparency is an important feature of science and it's ridiculous that we don't have to show our data.  It is absolutely the right thing to do.

@@

some more: `r citep(c(
bib["anagnostou2015when-da"],
bib["nosek2015scienti"],
bib["stodden2018an-empi"],
bib["budin-ljosne2014data-sh"],
bib["hate2015sweat-s"],
bib["naudet2018data-sh"],
bib["curty2017attitud"],
bib["linek2017data-sh"],
bib["longo2016data-sh"],
bib["berger2016iscbs-i"],
bib["chigusa2017state-o"],
bib["womack2015researc"],
bib["doi:10.1002/asi.23917"],
bib["plos-medicine-editors2016can-dat"],
bib["van-tuyl2016water-w"],
bib["vasilevsky2017reprodu"],
bib["doi:10.1002/asi.23336"],
bib["pearce2011data-sh"],
bib["alsheikh-ali2011public-"],
bib["vines2013mandate"],
bib["roche2014trouble"],
bib["roche2015public-"],
bib["lin2014recomme"],
bib["whitlock2016a-balan"],
bib["naughton-l2016making-"],
bib["teunis2015do-corr"],
bib["fetterman2015the-rep"]
))
`

@@

- IRB
- Survey questions
- Instructions to authors
- Contact corresponding code
- R files
- Raw data

@@

Everyone who took the survey.

@@

table <- relevant_jdap_adoption_dates[,c('JournalName', 'policy', 'policy_start')]
colnames(table) <- c('Journal', 'Policy', 'Adoption Date of JDAP or Equivalent Policy')
rownames(table) <- NULL
# kable(table)
```
